\chapter{Antenna Array and RF Front End}
\label{ch:rf-front-end}
\setsvg{svgpath=./img/rf-front-end/}
\graphicspath{{./img/rf-front-end/}}

This chapter details the design and characterisation of the antennas and RF front end; the first sub-system in the direction finder. The RF front end consists of low noise amplifiers (LNA), lower pass filters, and cabling. As discussed in the previous chapters, the aspects of the array which needs to be optimised for are:
\begin{itemize}
  \item Minimize the phase difference the RF path for each antenna. The DF algorithm is based on phase/time difference measurements and hence path mismatches will result in errors. Some phase difference can be calibrated out but the calibration routine will be most robust when the initial error is low.
  \item The spacing of the elements in the circular array needs to trade off between too large an element spacing and too small a spacing. Too large will result in phase ambiguity, to small will result in coupling between the elements as well as difficulty in measure time difference. The compromise is to make the array as large as possible before phase ambiguity becomes a problem.
\end{itemize}

The ADCs which were available for use in this project influenced the antenna and operating frequency band choice. They're explored more in Chapter 5 but will be briefly noted here as justification for the decisions taken here. The ADCs were two dual-input cards which sample two inputs in phase. They were clocked up to \SI{800}{\mega\hertz}. This implies 4 simultaneous inputs with a Nyquist frequency of \SI{400}{\mega\hertz}.\\

The Chapter will first discuss the design and construction of the antenna array, then move on to the RF front end. Finally, characterisation of the amplitude and phase performance of the RF front end will then be done. 


\input{./tex/42-antenna-array}
\input{./tex/45-lna}

\section{Summary}
This Chapter has detailed the design, construction and measurement of the antenna array and RF front end subsystem. It's shown how a 4 element array can be deformed from a square to produce ambiguity performance that's not far off of what's achieved by a 5 element array. Code was written to be able to introduce a coordinate system to elements from baseline distance measurements. 

The RF front end was built to provide some amplification in the band of interest and attenuation of out-of-band aliased signals. Mounting the circuitry on a board and making it battery powered will allow it to be taken into the field easily.

Measurements of the performance of the RF front end show it should work as expected.
